Introduction to Markov state modeling with the PyEMMA software --- v\versionnumber

### 2018-08-29 manuscript/manuscript.tex
[manuscript] append section about large systems

We utilize Jupyter~\cite{jupyter} notebooks to show code examples along with figures and interactive widgets to display molecules.
The user can install all necessary packages in one step using the \texttt{conda} command provided by the Anaconda Python stack (\url{https://anaconda.com}).
We recommend Anaconda because it resolves and installs dependencies as well as provides pre-compiled versions of common packages.
The tutorial installation contains a launcher command to start the Jupyter notebook server as well as the notebook files.

You can install the tutorial's dependencies in a new conda environment and start the notebook server via
\begin{verbatim}
conda create -n pyemma_tutorials
conda activate pyemma_tutorials
conda install -c conda-forge pyemma_tutorials
pyemma_tutorials
\end{verbatim}
or refer to \githubrepository{} for more detailed installation and usage instructions.

The data for the demonstrated test systems is downloaded upon the first use and is cached for future invocations of the tutorial.

@@

>>>>

We utilize Jupyter~\cite{jupyter} notebooks to show code examples along with figures and interactive widgets to display molecules.
The user can install all necessary packages in one step using the \texttt{conda} command provided by the Anaconda Python stack (\url{https://anaconda.com}).
We recommend Anaconda because it resolves and installs dependencies as well as provides pre-compiled versions of common packages.

The tutorial installation contains a launcher command to start the Jupyter notebook server as well as the notebook files.
The data for the demonstrated test systems is downloaded upon the first use and is cached for future invocations of the tutorial.

@@

\subsection{Markov models of large systems}
For modeling large systems, challenges arise that are mostly system dependent. 
One of them is that finding a state space discretization using e.g. $k$-means becomes difficult in very high dimensional spaces. 
It is thus important to choose a feature space and coordinate transform that yield a low dimensional representation of the slow processes.
Hidden Markov models might further help to overcome poor discretization to a certain extend.

In addition, the slowest process in a system as identified by a Markov model might not be the one a modeler is interested in. 
For instance, there might be a side chain flip that only occured once in a data set but has no biological relevance. 
This problem can often be mitigated by choosing a more specific set of features.

We explain how to deal with the technical challenges such as limited memory in the tutorials. 
More details on how to model complex systems with the techniques presented here are described by e.g. ~\cite{plattner_protein_2015,plattner_complete_2017}.
